\documentclass{report}

\input{~/dev/latex/template/preamble.tex}
\input{~/dev/latex/template/macros.tex}

\title{\Huge{Chapter 01 Review and Discuss}}
\author{\huge{Nathan Warner Constructed in LaTeX}}
\date{\huge{Jan 20, 2023}}

\begin{document}
    \maketitle
    \section{\Large{Review and Discuss Questions (Chapter 1)}}
    \line(1,0){470}
    \bigbreak \noindent 

    \qs{}{Define Digital Media}
    \pf{Answer}{}
        Digital Media refers to any medium that uses electronic devices 
        or the internet to store, create, or distribute information. 
        \textbf{A blend of audio, video, pictures, and text utilized to communicate through 
        electronic means.}
    \bigbreak \noindent     

    \qs{}{List the five commitments to learning that will help you to become suc-cessful in a digital media field.}
    \pf{Answer}{}
    \begin{enumerate}
        \item \textbf{Be flexible} 
        \item \textbf{Keep an open mind}
        \item \textbf{Use initiative}
        \item \textbf{Listen and read attentively}
        \item \textbf{Seek to aquire new knowledge and skills}
    \end{enumerate}
    \bigbreak \noindent   

    \qs{}{What are the six behaviors that make you more employable?}
    \pf{Answer}{}
    \begin{enumerate}
        \item \textbf{Good attendance} 
        \item \textbf{Promptness} 
        \item \textbf{Proper Attire} 
        \item \textbf{Clean and safe work environment} 
        \item \textbf{Appropriate voice} 
        \item \textbf{Pride} 
    \end{enumerate}
    \bigbreak \noindent

    \qs{}{What software tests are covered by an Adobe Certified Exam?}
    \pf{Answer}{The tests covered by an ACE}
    
    \noindent \textbf{Design Master:}
    \begin{itemize}
        \item Adobe Acrobat® Professional 
        \item Adobe InDesign®
        \item Adobe Illustrator
        \item Adobe Photoshop
    \end{itemize}
    
    \bigbreak \noindent 
    \textbf{Web Master}
    \begin{itemize}
        \item Adobe Acrobat Professional
        \item  Adobe Dreamweaver
        \item  Adobe Flash® Professional
        \item  Adobe Illustrator
        \item Adobe Photoshop
    \end{itemize}

    \bigbreak \noindent 
    \textbf{Video Master}
    \begin{itemize}
       \item Adobe AfterEffects®
       \item Adobe Flash Professional
       \item Adobe Illustrator
       \item Adobe Photoshop
       \item Adobe Premiere® Pro
    \end{itemize}
    \bigbreak \noindent
    
    \qs{}{List some options for backing up files}
    \pf{Answer}{}
    \noindent \textbf{There are 3 main methods for backing up files, as described in Chapter 1}
    \begin{itemize}
        \item Backups made on hardware such as flashdrives or a hard drive 
        \item Backups over the network
        \item Online backup, transfered over the internet to a system in a distant location
    \end{itemize}
    \bigbreak \noindent

    \qs{}{How can you protect yourself in an electronic world?}
    \pf{Answer}{}
    It is important to stay protected while online, this means 
    not revealing personal information and staying away from sites that are
    not secure and untrustworthy. \textbf{Here are some things you should look out for 
    and actions to take to prevent them}

    \bigbreak \noindent 
    \begin{itemize}
        \item Cyber Predators: Do not trust everyone you meet online, bring a trusted 
            adult if you wish to meet someone you met online
        \item Identity theft: Steer clear of shady webpages, do not put person information
            into any website that you do not believe to be secure or is not a credible company
        \item Keylogger: these are malicous files that are planted on a suspects computer 
            in order to log their keystrokes and potentially steal their passwords
        \item Maleware: Do not click shady download links and preform frequent scans
            of your file system to detect viruses.
    \end{itemize}
    \bigbreak \noindent

    \qs{}{How can you protect your computer and network?}
    \pf{Answer}{}
    In order to make sure your computer and network is secure it is important to understand 
    what makes a password secure, it is also important to understand the use of data encryption. 
    Lastly, you should ensure that your network is not available to the public.
    \bigbreak \noindent

    \qs{}{Explain what defines a strong password}
    \pf{Answer}{}
    \begin{enumerate}
        \item Have a minimum of eight characters 
        \item Use both upper and lower case letters
        \item Use at least one special character
    \end{enumerate}
    \bigbreak \noindent

    \qs{}{What is the purpose of ergonomics?}
    \pf{Answer}{} 
    Ergonomics is the study of how people interact with their environment, 
    particularly in the context of work. Its goal is to design products, systems, and 
    processes that fit the human body and its cognitive abilities. The purpose of ergonomics 
    is to improve comfort, health, and safety, and to increase productivity by reducing the 
    risk of injury or discomfort caused by improper fit between the worker and the work 
    environment. It can also be applied in non-work contexts, such as in home and 
    transportation design.

    \bigbreak \noindent 

    \qs{}{What steps can you take to prevent repetitive stress injury?}
    \pf{Answer}{} 
    \noindent \textbf{Ways to prevent repetitive stress injury include:}
    \begin{itemize}
        \item Your keyboard should be at elbow height and even with the front edge of your desk.
        \item Your monitor should be positioned to avoid glare and be located at least an arm’s length away.
        \item Your chair should have a good backrest.•Your back should be touching the backrest at all times.
        \item Your feet should be flat on the floor (or use a footrest).
        \item You should sit up straight, keeping your head and neck as straight as possible
    \end{itemize}

\end{document}
